Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-14 paper/reviewers-response.Rmd

> "A few references require editing to journal style (e.g. remove initials for many citations)"

*Accepted and changed*. We have corrected all citations. One of them, however, still shows an author's first name initial, as it is necessary to distinguish two authors with the same last name (\lr{M-R2-citation-with-name}).

> "*L388*: remove repeated 'other'. I suggest that the authors re-write this sentence to improve clarity."

*Accepted and changed*. We have removed the second 'other'. As suggested, we have rewritten the sentence to improve clarity (\lr{M-R2-structural-controllability}). It now reads as follows: "First, structural controllability emphasizes that the effect a species has on other species is not independent of the effects that the other species have in the community".

### 2019-01-14 paper/manuscript.Rmd
Improve clarity of sentence with two others about the effect of species
on each other

Other conceptual differences between structural controllability and centrality metrics provide three key insights into the conservation of ecological networks. 
\R{R2-structural-controllability} First, structural controllability emphasizes that the effect a species has on the abundance of other species is not independent of the effects of those other species in their community. 
The rankings provided by centrality metrics and other heuristics fail to account for the collective influence of several species at once. 
Second, it demonstrates that to ensure the persistence of a community it is often necessary to consider the abundances of more than a single species, even when full control is infeasible or undesired (for example `r round(sum(crit$n_crit > 1)/nrow(crit)*100)`% of our communities contained more than one critical species). 
Third, structural controllability explicitly acknowledges the existence of multiple management strategies and some will be better than others depending on the context.
Approaches to prioritise species for conservation and reintroduction based on traits or centrality are still useful and are likely to overlap with species' control capacity [@pires_friendship_2017; @devoto_understanding_2012]. 
Stepping back, our results also provide support to the idea that management decisions should not be based on a single technique but indicate that focusing on ecosystem processes and interactions may be more effective than traditional ranking-based approaches [@harvey_bridging_2017].

>>>>

Other conceptual differences between structural controllability and centrality metrics provide three key insights into the conservation of ecological networks. 
\R{R2-structural-controllability} First, structural controllability emphasizes that the effect a species has on other species is not independent of the effects that the other species have in the community. 
The rankings provided by centrality metrics and other heuristics fail to account for the collective influence of several species at once. 
Second, it demonstrates that to ensure the persistence of a community it is often necessary to consider the abundances of more than a single species, even when full control is infeasible or undesired (for example `r round(sum(crit$n_crit > 1)/nrow(crit)*100)`% of our communities contained more than one critical species). 
Third, structural controllability explicitly acknowledges the existence of multiple management strategies and some will be better than others depending on the context.
Approaches to prioritise species for conservation and reintroduction based on traits or centrality are still useful and are likely to overlap with species' control capacity [@pires_friendship_2017; @devoto_understanding_2012]. 
Stepping back, our results also provide support to the idea that management decisions should not be based on a single technique but indicate that focusing on ecosystem processes and interactions may be more effective than traditional ranking-based approaches [@harvey_bridging_2017].
